### 2010-06-08 docs/introduction/introduction.tex
characteristic -> primitive
update multilevel paper ref

\noindent The current version of the algorithm is described in our
multilevel paper:
\begin{itemize}
\item {\em MAESTRO: An Adaptive Low Mach Number Hydrodynamics Algorithm for Stellar
  Flows,} A. Nonaka, A. S. Almgren, J. B. Bell, M. J. Lijewski, C. M. Malone,
  \& M. Zingale 2010, submitted to ApJ
  (henceforth ``the multilevel paper'')
\end{itemize}

@@

Most astrophysical hydrodynamics codes
(e.g.\ CASTRO~\cite{castro} or FLASH~\cite{flash}) solve the
compressible Euler equations, which can be written in the form:
\begin{equation}
U_t + \nabla \cdot F(U) = 0
\end{equation}
where U is the vector of conserved quantities, $U = (\rho, \rho u,
\rho E)$, with $\rho$ the density, $u$ the velocity, and $E$ the total
energy per unit mass.  This system of equations can be expressed 
as a system of advection equations:
\begin{equation}
w_t + A(w) w_x = 0
\end{equation}
where $w$ are called the characteristic variables, and $A$ is the
Jacobian, $A \equiv \partial F / \partial U$.  The eigenvalues of the
matrix $A$ are the characteristic speeds---the speeds at which
information propagates.  For the Euler equations, these are $u$ and $u
\pm c$, where $c$ is the sound speed.  Solution methods for the
compressible equations make use of this wave-nature to compute fluxes
at the interfaces of grid cells to update the state in time.  An
excellent introduction to these methods is provided by LeVeque's book
\cite{leveque}.  The timestep for these methods is limited by the time
it takes for maximum characteristic speed to traverse one grid cell.
For very subsonic flows, this means that the timestep is dominated by
the propagation of soundwaves, which may not be important to the
overall dynamics of the flow.

>>>>

\noindent The current version of the algorithm is described in our
multilevel paper:
\begin{itemize}
\item {\em MAESTRO: An Adaptive Low Mach Number Hydrodynamics Algorithm for Stellar
  Flows,} A. Nonaka, A. S. Almgren, J. B. Bell, M. J. Lijewski, C. M. Malone,
  \& M. Zingale 2010, ApJS, 188, 358 (henceforth ``the multilevel paper'')
\end{itemize}

@@

Most astrophysical hydrodynamics codes
(e.g.\ CASTRO~\cite{castro} or FLASH~\cite{flash}) solve the
compressible Euler equations, which can be written in the form:
\begin{equation}
U_t + \nabla \cdot F(U) = 0
\end{equation}
where U is the vector of conserved quantities, $U = (\rho, \rho u,
\rho E)$, with $\rho$ the density, $u$ the velocity, and $E$ the total
energy per unit mass.  This system of equations can be expressed 
as a system of advection equations:
\begin{equation}
q_t + A(q) q_x = 0
\end{equation}
where $q$ are called the primitive variables, and $A$ is the
Jacobian, $A \equiv \partial F / \partial U$.  The eigenvalues of the
matrix $A$ are the characteristic speeds---the speeds at which
information propagates.  For the Euler equations, these are $u$ and $u
\pm c$, where $c$ is the sound speed.  Solution methods for the
compressible equations make use of this wave-nature to compute fluxes
at the interfaces of grid cells to update the state in time.  An
excellent introduction to these methods is provided by LeVeque's book
\cite{leveque}.  The timestep for these methods is limited by the time
it takes for maximum characteristic speed to traverse one grid cell.
For very subsonic flows, this means that the timestep is dominated by
the propagation of soundwaves, which may not be important to the
overall dynamics of the flow.
